Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-09-05 Ben_Manuscripts/Paper1/Outline.tex
editing results and discussion

  To discern the composition of the monomer layers, we ran simulations of 
  systems created with 4 - 8 monomers per layer.
  \begin{itemize}
  	\item Both the sandwiched and parallel displaced configurations were tested.
	\item All systems remained stable for at least 50 ns.
        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
        %MRS: are they all equally stable? I though you had some additional information on this. Are you saving it for later?  
        %MRS: remind people where the uncertainty comes from.

	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
	Systems built with 5 monomers in each layer equilibrate to a pore spacing
	that is most consistent with the experimental value of 4.12 nm derived from
	SAXS measurements (Figure~\ref{fig:SAXS}).
	\item We verified that the system stays partitioned into layers by plotting 
	pair correlation functions calculated between aromatic rings along the length
	of the pores (Fig~\ref{fig:zdf}).
        %MRS: explain how that conclusion was reached (perioic with period X, minima was Y percent lower than mean, maxima was Y percent higher).
	\item The remainder of this discussion will focus on the analysis of systems
	built with 5 monomers per layer. 
  \end{itemize}

@@

  Experimental WAXS measurements encode all remaining structural details. 
  %MRS: also encodes the pore spacing
  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
	attributed to pi-pi stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-pi.
        %MRS: why R in R-pi? for reflection?
	\item A weak intensity line is located at exactly half the qz value of
	R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
        %MRS: or could use \angstrom$^-1$ instead of \textsuperscript{-1} 
	real space periodic spacing of 7.4 \angstrom. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
	corresponds to 4.5 \angstrom which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along qz = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}[t]{0.47\linewidth}
		\centering
		\raisebox{.2\textwidth}{%
		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
		}
		\caption{}\label{fig:WAXS}
	\end{subfigure}
	\begin{subfigure}[t]{0.43\linewidth}
		\centering
	%	\vspace{12mm}
		\includegraphics[width=\linewidth]{SAXS.png}
		\caption{}\label{fig:SAXS}
	\end{subfigure}
	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
        %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
  \end{figure}

>>>>

  To discern the composition of the monomer layers, we ran simulations of 
  systems created with 4 - 8 monomers per layer.
  \begin{itemize}
  	\item Both the sandwiched and parallel displaced configurations were tested.
	\item All systems are stable after 50 ns of simulation.  % BJC: edited this for clarity
        %MRS: you only ran for 50 ns, or after 50 ns some of them started to destabilize?  Is the point you are making that they are ALL pretty stable, or all at least a little stable.   
        %MRS: are they all equally stable? I though you had some additional information on this. Are you saving it for later?  
        %MRS: remind people where the uncertainty comes from.
	%BJC: It looks like the 7 and 8 monomer systems were only run for 50 ns. The 4 monomer system was run for 200 ns. 5 and 6 have a lot of data. 7 and 8 flattened pretty quickly, so at the time I figured it wasn't worth continuing. But I'll extend them just to be thorough.

	\item Table ~\ref{table:p2p} shows the pore spacing for all systems tested. 
	Systems built with 5 monomers in each layer equilibrate to a pore spacing
	that is most consistent with the experimental value of 4.12 nm derived from
	SAXS measurements (Figure~\ref{fig:SAXS}).
	\item We verified that the system stays partitioned into layers by plotting 
	pair correlation functions calculated between aromatic rings along the length
	of the pores (Fig~\ref{fig:zdf}).
        %MRS: explain how that conclusion was reached (perioic with period X, minima was Y percent lower than mean, maxima was Y percent higher).
	%BJC: okay, need to run some calculations here.
	\item The remainder of this discussion will focus on the analysis of systems
	built with 5 monomers per layer. 
  \end{itemize}

@@

  Experimental WAXS measurements encode all structural details. 
  %MRS: also encodes the pore spacing
  %BJC: got rid of 'remaining' in 'remaining structural details'
  %BJC: I'm not exactly sure where to place this paragraph. Maybe it can go in methods?
  \begin{itemize}
  	\item There are five major features present in the 2D experimental 
	pattern which our model intends to reproduce (Figure~\ref{fig:WAXS}).
	\item The first is located at qz = 1.7 \angstrom \textsuperscript{-1},
	corresponding to a real spacing of 3.7 \angstrom. The reflection is 
	attributed to pi-pi stacking between aromatic rings in the direction
	perpendicular to the membrane plane, or z-axis. For simplicity, this 
	reflection will be referred to as R-pi.
        %MRS: why R in R-pi? for reflection?
	%BJC: yes, R = reflection
	\item A weak intensity line is located at exactly half the qz value of
	R-pi (qz = 0.85 \angstrom$^-1$), corresponding to a 
        %MRS: or could use \angstrom$^-1$ instead of \textsuperscript{-1} 
	real space periodic spacing of 7.4 \angstrom. This reflection has been 
	interpreted  as 2\textsubscript{1} helical ordering of aromatic rings 
	along the z axis meaning if the positions of the aromatic rings can
	be traced by a helix, then for each turn in the helix, there should be
	two aromatic rings. For this reason it will be referred to as R-helix.
	\item A third major reflection is marked by a low intensity ring located
	at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
	corresponds to 4.5 \angstrom which is characteristic of the average 
	spacing between packed alkane chains. This reflection will be called R-alkanes.
	\item Within R-alkanes, are four spots of higher intensity which 
	will be called R-spots. All are located $\approx 40$ degrees from the qz axis
	in their respective quadrants. In many liquid crystal systems this can be
	explained by the tilt angle of the alkane chains with respect to the xy plane. % BJC: Reference
	\item The final major reflections correspond to the spacing and symmetry of 
	the d\textsubscript{100} plane which can be related to the distance between
	pores. The feature, which will be called R-pores, is characterized by dots 
	along qz = 0. The spacing between dots is indicative of the hexagonal 
	symmetry of the packed pores. It is easiest to interpret the data by 
	radially integrating the 2D data to get a 1D curve which is shown in Figure~\ref{fig:SAXS}.
  \end{itemize}

  \begin{figure}[!ht]
	\centering
	\begin{subfigure}[t]{0.47\linewidth}
		\centering
		\raisebox{.2\textwidth}{%
		\includegraphics[width=\linewidth]{WAXS_soft_confined.png}
		}
		\caption{}\label{fig:WAXS}
	\end{subfigure}
	\begin{subfigure}[t]{0.43\linewidth}
		\centering
	%	\vspace{12mm}
		\includegraphics[width=\linewidth]{SAXS.png}
		\caption{}\label{fig:SAXS}
	\end{subfigure}
	\caption{(a) 2D wide angle X-ray scattering gives details about repeating
	features less than 1 nanometer apart. (b) 1D small angle X-ray scattering 
	indicates hexagonal packing of pores as well as the spacing between pores.}\label{fig:SWAXS}
        %MRS: maybe compare the 2D and 1D from simulation here as well?  Need to state the above figure is from another paper (I think at least the 1D is?)
	%BJC: 1D is from a Yale paper. I'm going to remake the figure from the raw data but will reference that
	%BJC: The simulated 1D shows the right peaks, but the resolution makes it kind of pointy. I'll let you take a look at it but maybe it belongs in the supplemental
  \end{figure}
